The pollination trade-off

### 2019-03-13 paper/manuscript.Rmd
Some edits to the discussion

Our results suggest that the community context plays a central role in determining competition for pollination. 
First, we found that the costs of pollinator sharing are pervasive. In particular, we found that a significant proportion of species undergoes overall neutral or competitive effects from animal-mediated pollination. 
Second, we found that plants are able to minimise the intensity of this competition using multiple strategies, however, conspecific and heterospecific pollen deposition are tightly coupled and therefore these strategies are likely to involve a trade-off between the quantity and quality of pollination. 
Third, we found that these strategies are strongly shaped by the community context, this is, the same plant species can adopt dramatically different strategies depending on the community it belongs to.

\R{disc-facil-comp}Both of the tests we used to identify the effect of animal-mediated pollination suggested the same outcome: that overall facilitation is only experienced by a minority of species in a community. 
Although a recent study already suggested a wide range of outcomes in a multi-species context [@tur_evaluating_2016], the factors determining why some species experience more competition than others were not understood. 
Here we show that the prevalence of neutral and competitive effects of animal-mediated pollination can be, at least partially, explained by the trade-offs that minimising competition involves.

These trade-offs were most evident precisely in the strategies that most strongly modulate pollen deposition. 
We found that the strategies that increased the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition. 
Adopting a strategy of high visitation increases the rates of conspecific pollen deposition at the expense of a reduction in the quality of pollination even when the visitors carry a high proportion of conspecific pollen. 
Similarly, adopting a strategy of high abundance reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
Our results corroborate the importance that previous studies have attributed to the role that visitation and abundance play at determining competition for pollination [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008]. 
The fact that they also involve a trade-off between the quantity and quality of pollination might explain the often contrasting results that these studies, based on two or three species systems obtained.

Simultaneously, because visitation, pollen production and abundance are correlated [@sargent_role_2006], the trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between increasing conspecific pollen and reduce heterospecific pollen deposition. 
The relatively wide range of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
While some plant species experience a large reduction on seed set due to heterospecific pollen deposition, some others are relatively insensitive to heterospecific pollen but are greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].

>>>>

All else being equal, our results suggest that community context plays a central role in determining net cost or benefit of sharing pollinators.
First, we found that the costs of pollinator sharing are pervasive. 
In particular, we found that a significant proportion of species experiences overall neutral or competitive effects from animal-mediated pollination. 
Second, we found that multiple ecological factors can modulate the intensity of this competition; however, conspecific and heterospecific pollen deposition are tightly coupled and therefore these factors are likely to involve a trade-off between the quantity and quality of pollination. 
Third, we found that the way these factors influence competition is strongly shaped by the community context, this is, if collectively these factors are used to define a niche of competition for pollination, the same plant species can occupy dramatically different niches depending on the community it belongs to.

Both of the tests we used to identify the effect of animal-mediated pollination suggested the same outcome: that net facilitation is only experienced by a fraction of species in a community. 
A recent study also suggested a wide range of outcomes in a multi-species context [@tur_evaluating_2016]. 
However, the factors explaining why some species experience more competition than others were not understood. 
Here we show that the prevalence of neutral and competitive effects of animal-mediated pollination can be at least partially explained by the trade-offs that minimising competition can involve.  
These trade-offs were most evident in precisely the factors that most strongly modulate pollen deposition. 
Specifically, we found that the factors related to the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition. 
At the same time, receiving high visitation increases the absolute levels of conspecific pollen deposition but increasses heterospeicific deposition to a greater extent even when the visitors are likely carry a high proportion of conspecific pollen. 
Similarly, being abundant reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
Multiple studies recognise the importance of visitation and abundance to competition for pollination, however, some suggest a positive effect on the pollination service while some others a negative one [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008]. 
Our results corroborate the importance of these two factors, and show that the contrsating results obtained by earlier studies could be explained by the trade-offs involved.

Simultaneously, because visitation, pollen production and abundance are correlated [@sargent_role_2006], the trade-offs also suggest that plants must reach a fine balance between increasing conspecific pollen and reduce heterospecific pollen deposition to minimise competition for pollination. 
The relatively broad distribution of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
Indeed, some plant species experience a large reduction in seed set due to heterospecific pollen deposition, while others are relatively insensitive to heterospecific pollen but greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
